---
title: "Code"
author: "Michelle Dai"
date: '2022-05-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Appendix: Data Details


Source of data: https://www.kaggle.com/datasets/imakash3011/customer-personality-analysis?select=marketing_campaign.csv

ID: Customer's unique identifier
Year_Birth: Customer's birth year
Education: Customer's education level
Marital_Status: Customer's marital status
Income: Customer's yearly household income
Kidhome: Number of children in customer's household
Teenhome: Number of teenagers in customer's household
Dt_Customer: Date of customer's enrollment with the company
Recency: Number of days since customer's last purchase
Complain: 1 if the customer complained in the last 2 years, 0 otherwise

MntWines: Amount spent on wine in last 2 years
MntFruits: Amount spent on fruits in last 2 years
MntMeatProducts: Amount spent on meat in last 2 years
MntFishProducts: Amount spent on fish in last 2 years
MntSweetProducts: Amount spent on sweets in last 2 years
MntGoldProds: Amount spent on gold in last 2 years

NumDealsPurchases: Number of purchases made with a discount
AcceptedCmp1: 1 if customer accepted the offer in the 1st campaign, 0 otherwise
AcceptedCmp2: 1 if customer accepted the offer in the 2nd campaign, 0 otherwise
AcceptedCmp3: 1 if customer accepted the offer in the 3rd campaign, 0 otherwise
AcceptedCmp4: 1 if customer accepted the offer in the 4th campaign, 0 otherwise
AcceptedCmp5: 1 if customer accepted the offer in the 5th campaign, 0 otherwise
Response: 1 if customer accepted the offer in the last campaign, 0 otherwise

NumWebPurchases: Number of purchases made through the company’s website
NumCatalogPurchases: Number of purchases made using a catalogue
NumStorePurchases: Number of purchases made directly in stores
NumWebVisitsMonth: Number of visits to company’s website in the last month

TotalPurchase is the sum of NumWebPurchases, NumCatalogPurchases, and NumStorePurchases.


## References

Austin, Peter C. “An Introduction to Propensity Score Methods for Reducing the Effects of Confounding in Observational Studies.” Multivariate Behavioral Research, vol. 46, no. 3, 2011, pp. 399–424., https://doi.org/10.1080/00273171.2011.568786. 

Malcolm Barrett, Lucy D’Agostino McGowan. “Causal Inference in R.” Causal Inference in R, 8 Mar. 2022, https://www.r-causal.org/. 


## Code



### Data Description and Problem Identified


```{r, results='hide', message=FALSE, warning=FALSE}
library(causaldata)
library(dbplyr)
library(ggdag)
library(tidyverse)
library(broom)
library(visdat)
data <- read.csv(file="marketing_campaign.csv")
```

```{r, results='hide'}
data$TotalPurchase <- data$NumWebPurchases+ data$NumCatalogPurchases+data$NumStorePurchases
data_sub <- data %>% select(Year_Birth, Education, Marital_Status, Income, Kidhome, Teenhome, Recency, Complain, NumDealsPurchases, TotalPurchase, NumWebVisitsMonth)
```

```{r, results='hide'}
purchase <- dagify(
  NumWebVisitsMonth ~ Year_Birth + Education +Marital_Status+ Kidhome + Teenhome + Recency + NumDealsPurchases,
  TotalPurchase ~ Marital_Status + Income + Kidhome + Teenhome + Recency + Complain + NumDealsPurchases,
  exposure = "NumWebVisitsMonth",
  outcome = "TotalPurchase",
  labels = c(
    NumWebVisitsMonth = "#Web Visit Last Month",
    Year_Birth = "Birth Year",
    Education = "Education",
    Marital_Status = "Marital Status",
    Kidhome = "#Kids at Home",
    Teenhome = "#Teenagers at Home",
    Recency = "#Days since Last Purchase",
    NumDealsPurchases = "#Purchase using Discount",
    Income = "Income",
    TotalPurchase = "Total Purchase",
    Complain = "Complain"
  )
)
ggdag_status(purchase, use_labels = "label", text = FALSE) +
  guides(fill = "none", color = "none")

dagify(
  NumWebVisitsMonth ~ Year_Birth + Education +Marital_Status+ Kidhome + Teenhome + Recency + NumDealsPurchases,
  TotalPurchase ~ Marital_Status + Income + Kidhome + Teenhome + Recency + Complain + NumDealsPurchases,
  exposure = "NumWebVisitsMonth",
  outcome = "TotalPurchase",
  labels = c(
    NumWebVisitsMonth = "#Web Visit Last Month",
    Year_Birth = "Birth Year",
    Education = "Education",
    Marital_Status = "Marital Status",
    Kidhome = "#Kids at Home",
    Teenhome = "#Teenagers at Home",
    Recency = "#Days since Last Purchase",
    NumDealsPurchases = "#Purchase using Discount",
    Income = "Income",
    TotalPurchase = "Total Purchase",
    Complain = "Complain"
  )
) %>%
ggdag_adjustment_set(text_col = "black")
```


### Missing Data Imputation


```{r, message=FALSE, warning=FALSE, results='hide'}
vis_dat(data_sub) + labs(title = "Figure 1: Missing Data")
```

```{r, warning=FALSE, message=FALSE, results='hide'}
library(mice)
library(MatchThem)
library(survey)
set.seed(1)
```

```{r, warning=FALSE, message=FALSE, results='hide'}
lm(Recency~Income, data = data_sub) %>%
  tidy()
data_sub_imp <- mice(data_sub, 5, "pmm", printFlag = FALSE)

data_sub_complete <- complete(data_sub_imp)

lm(Recency~Income, data = data_sub_complete) %>%
  tidy()
```

```{r, results='hide'}
data_sub_complete <- data_sub_complete %>% 
  mutate(Education = ifelse(Education == "2n Cycle", 0, Education))%>% 
  mutate(Education = ifelse(Education == "Basic", 1, Education)) %>% 
  mutate(Education = ifelse(Education == "Graduation", 2, Education)) %>% 
  mutate(Education = ifelse(Education == "Master", 3, Education)) %>% 
  mutate(Education = ifelse(Education == "PhD", 4, Education)) %>% 
  mutate(Marital_Status = ifelse(Marital_Status == "Single", 0, Marital_Status)) %>% 
  mutate(Marital_Status = ifelse(Marital_Status == "Together", 1, Marital_Status))%>% 
  mutate(Marital_Status = ifelse(Marital_Status == "Married", 2, Marital_Status))%>% 
  mutate(Marital_Status = ifelse(Marital_Status == "Divorced", 3, Marital_Status))%>% 
  mutate(Marital_Status = ifelse(Marital_Status == "Widow", 4, Marital_Status))%>% 
  mutate(Marital_Status = ifelse(Marital_Status == "Alone", 5, Marital_Status))%>% 
  mutate(Marital_Status = ifelse(Marital_Status == "Absurd", 6, Marital_Status))%>% 
  mutate(Marital_Status = ifelse(Marital_Status == "YOLO", 7, Marital_Status))
  
data_continuous <- data_sub_complete

data_sub_complete <- data_sub_complete %>% mutate(NumWebVisitsMonth = ifelse(NumWebVisitsMonth>=6, 1, 0))
```



### Propensity Score Model {.tabset}


```{r, message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(dplyr)
library(broom)
library(smd)
library(gtsummary)
library(survey)

data_sub_complete %>%
  tbl_summary(
    by = NumWebVisitsMonth, 
    include = c(
      "Year_Birth", "Education", "Marital_Status", "Kidhome", "Teenhome", "Recency", "NumDealsPurchases")) %>%
  add_overall()
```


#### Unweighted


```{r, results='hide', message=FALSE, warning=FALSE}
data_sub_complete <- 
  glm(NumWebVisitsMonth ~ Year_Birth + as.factor(Education) +as.factor(Marital_Status)+ Kidhome + Teenhome + Recency + NumDealsPurchases, 
    data = data_sub_complete,
    family = binomial()) %>%
  augment(type.predict = "response",
          data = data_sub_complete) # concatenation
data_sub_complete %>%
  select(NumWebVisitsMonth, .fitted)
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ggplot(data_sub_complete, aes(x= .fitted, fill = as.factor(NumWebVisitsMonth))) + 
  geom_histogram(bins = 30) +geom_vline(xintercept = median(data_sub_complete[data_sub_complete$NumWebVisitsMonth == 0, ]$.fitted), linetype="twodash", 
                color = "red", size=1)+geom_vline(xintercept = median(data_sub_complete[data_sub_complete$NumWebVisitsMonth == 1, ]$.fitted), linetype="twodash", 
                color = "turquoise4", size=1)+
  labs(x="Propensity Score", y="Count", title= "Figure 2: Distribution of Propensity Score before Weighting")

#median(data_sub_complete[data_sub_complete$NumWebVisitsMonth == 0, ]$.fitted)
#median(data_sub_complete[data_sub_complete$NumWebVisitsMonth == 1, ]$.fitted)
```

```{r, message=FALSE, warning=FALSE, results='hide'}
library(rsample)
library(PSW)

#fit inverse probablity weight model
fit_ipw <- function(split, ...) {
  .df <- analysis(split)
  # fit propensity score model
  propensity_model <- glm(
    NumWebVisitsMonth ~ Year_Birth + as.factor(Education) +as.factor(Marital_Status)+ Kidhome + Teenhome + Recency + NumDealsPurchases,
    data = .df,
    family = binomial()
  )
  # calculate inverse probability weights
  .df <- propensity_model %>% 
    augment(type.predict = "response", data = .df)
  # outcome model 
  lm(TotalPurchase ~ NumWebVisitsMonth, data = .df) %>% 
    tidy()
}

# fit ipw model to bootstrapped samples
ipw_results <- bootstraps(data_sub_complete, 1000, apparent = TRUE) %>% 
  mutate(results = map(splits, fit_ipw))
```

```{r, message=FALSE, warning=FALSE, results='hide'}
# get t-statistic-based CIs
boot_estimate <- int_t(ipw_results, results) %>%
  filter(term == c("(Intercept)", "NumWebVisitsMonth"))
boot_estimate
```


#### ATO Weighted


```{r, message=FALSE, warning=FALSE, results='hide'}
data_sub_complete <- glm(NumWebVisitsMonth ~ Year_Birth + as.factor(Education) +as.factor(Marital_Status)+ Kidhome + Teenhome + Recency + NumDealsPurchases,
                         data=data_sub_complete, family = binomial()) %>%
  augment(data_sub_complete, type.predict = "response") %>%
  mutate(wt_ato = (1 - NumWebVisitsMonth)* .fitted + NumWebVisitsMonth * (1 - .fitted))
```

```{r, message=FALSE, warning=FALSE, results='hide'}
des <- svydesign(
  ids = ~1,
  data =  data_sub_complete,
  weight = ~ wt_ato
)

des %>%
  tbl_svysummary(
    by = NumWebVisitsMonth, 
    include = c(
      "Year_Birth", "Education", "Marital_Status", "Kidhome", "Teenhome", "Recency", "NumDealsPurchases")) %>%
  add_overall()
```

```{r, message=FALSE, warning=FALSE, results='hide'}
for_plot <- data_sub_complete %>% distinct() %>%
  pivot_wider(names_from = NumWebVisitsMonth,
              values_from = .fitted,
              names_prefix = "NumWebVisitsMonth_p")
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ggplot(for_plot) +
  geom_histogram(bins = 50,
                 aes(x = NumWebVisitsMonth_p1, 
                     weight = wt_ato),  
                 fill = "cornflower blue") +
  geom_histogram(bins = 50,
                 aes(x = NumWebVisitsMonth_p0,
                     weight = wt_ato,
                     y = - stat(count)),
                 fill = "orange") + 
  scale_y_continuous("Count", label = abs) + 
  scale_x_continuous("Propensity Score (ATO Weighted)") +
  geom_label(
    label = "Visit >= 6", 
    x = 0.1,
    y = 10,
  )+
    geom_label(
    label = "Visit < 6", 
    x = 0.1,
    y = -10,
  )+ labs(title= "Figure 3: Distribution of Propensity Score (ATO Weighted)")
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ecdf_1 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 1) %>%
  arrange(Income) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))

ecdf_0 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 0) %>%
  arrange(Income) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ggplot(ecdf_1, aes(x = Income, y = cum_pct_ato, color = "Yes")) +
  geom_line() +
  geom_line(data = ecdf_0, 
            aes(x = Income, y = cum_pct_ato, color = "No")) + labs(x = "Income after ATO weighting", y = "(ATO Weighted) Percent <= x", title="Figure 4: ATO Weighted ECDF for Income", color = "NumWebVisitsMonth")
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ecdf_1 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 1) %>%
  arrange(Year_Birth) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))

ecdf_0 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 0) %>%
  arrange(Year_Birth) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ggplot(ecdf_1, aes(x = Year_Birth, y = cum_pct_ato, color = "Yes")) +
  geom_line() +
  geom_line(data = ecdf_0, 
            aes(x = Year_Birth, y = cum_pct_ato, color = "No")) + labs(x = "Year_Birth after ATO weighting", y = "(ATO Weighted) Percent <= x", title="Figure 5: ATO Weighted ECDF for Year_Birth", color = "NumWebVisitsMonth")
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ecdf_1 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 1) %>%
  arrange(Recency) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))

ecdf_0 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 0) %>%
  arrange(Recency) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ggplot(ecdf_1, aes(x = Recency, y = cum_pct_ato, color = "Yes")) +
  geom_line() +
  geom_line(data = ecdf_0, 
            aes(x = Recency, y = cum_pct_ato, color = "No")) + labs(x = "Recency after ATO weighting", y = "(ATO Weighted) Percent <= x", title="Figure 6: ATO Weighted ECDF for Recency", color = "NumWebVisitsMonth")
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ecdf_1 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 1) %>%
  arrange(Kidhome) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))

ecdf_0 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 0) %>%
  arrange(Kidhome) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ggplot(ecdf_1, aes(x = Kidhome, y = cum_pct_ato, color = "Yes")) +
  geom_line() +
  geom_line(data = ecdf_0, 
            aes(x = Kidhome, y = cum_pct_ato, color = "No")) + labs(x = "Kidhome after ATO weighting", y = "(ATO Weighted) Percent <= x", title="Figure 7: ATO Weighted ECDF for Kidhome", color = "NumWebVisitsMonth")
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ecdf_1 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 1) %>%
  arrange(Teenhome) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))

ecdf_0 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 0) %>%
  arrange(Teenhome) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ggplot(ecdf_1, aes(x = Teenhome, y = cum_pct_ato, color = "Yes")) +
  geom_line() +
  geom_line(data = ecdf_0, 
            aes(x = Teenhome, y = cum_pct_ato, color = "No")) + labs(x = "Teenhome after ATO weighting", y = "(ATO Weighted) Percent <= x", title="Figure 8: ATO Weighted ECDF for Teenhome", color = "NumWebVisitsMonth")
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ecdf_1 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 1) %>%
  arrange(NumDealsPurchases) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))

ecdf_0 <- data_sub_complete %>%
  filter(NumWebVisitsMonth == 0) %>%
  arrange(NumDealsPurchases) %>%
  mutate(cum_pct_ato = cumsum(wt_ato) / sum(wt_ato))
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ggplot(ecdf_1, aes(x = NumDealsPurchases, y = cum_pct_ato, color = "Yes")) +
  geom_line() +
  geom_line(data = ecdf_0, 
            aes(x = NumDealsPurchases, y = cum_pct_ato, color = "No")) + labs(x = "NumDealsPurchases after ATO weighting", y = "(ATO Weighted) Percent <= x", title="Figure 9: ATO Weighted ECDF for NumDealsPurchases", color = "NumWebVisitsMonth")
```

```{r, message=FALSE, warning=FALSE, results='hide'}
smds <- data_sub_complete %>%
  summarise(
    across(
      c("Year_Birth", "Education", "Kidhome", "Teenhome", "Recency", "NumDealsPurchases"),
      list(
        unweighted = ~smd(.x, NumWebVisitsMonth)$estimate,
        ato.weighted = ~smd(.x, NumWebVisitsMonth, w = wt_ato)$estimate
      )
    )
  )


smds %>%
  pivot_longer(
    everything(),
    values_to = "SMD",
    names_to = c("variable", "Method"),
    names_pattern = "(.*)_(.*)") %>%
  arrange(desc(Method), abs(SMD)) %>%
  mutate(variable = fct_inorder(variable)) -> for_plot
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ggplot(for_plot, aes(x = abs(SMD), y=variable, group = Method, color= Method))+ labs(x = "Standarized Mean Difference", y="Variables", title = "Figure 10: Love Plot") +
  geom_line(orientation = "y") +
  geom_point() +
  geom_vline(xintercept = 0.1, lty = 2, color = "black", size =0.1)
```

```{r, message=FALSE, warning=FALSE, results='hide'}
library(rsample)
library(PSW)
#fit inverse probablity weight model
fit_ipw <- function(split, ...) {
  .df <- analysis(split)
  # fit propensity score model
  propensity_model <- glm(
    NumWebVisitsMonth ~ Year_Birth + as.factor(Education) +as.factor(Marital_Status)+ Kidhome + Teenhome + Recency + NumDealsPurchases,
    data = .df,
    family = binomial()
  )
  # calculate inverse probability weights
  .df <- propensity_model %>% 
    augment(type.predict = "response", data = .df) %>% 
    mutate(wt_ato = (1 - NumWebVisitsMonth)* .fitted + NumWebVisitsMonth * (1 - .fitted))
  # fit correctly bootsrapped ipw model
  # outcome model 
  lm(TotalPurchase ~ NumWebVisitsMonth, data = .df, weights = wt_ato) %>% 
    tidy()
}

# fit ipw model to bootstrapped samples
ipw_results <- bootstraps(data_sub_complete, 1000, apparent = TRUE) %>% 
  mutate(results = map(splits, fit_ipw))
```

```{r, message=FALSE, warning=FALSE, results='hide'}
# get t-statistic-based CIs
boot_estimate <- int_t(ipw_results, results) %>%
  filter(term == c("(Intercept)", "NumWebVisitsMonth"))
boot_estimate
```



#### Continuous Exposure IPW


```{r, results='hide'}
# the numerator
mod_num <- lm(NumWebVisitsMonth ~ 1, data = data_continuous)

num <- dnorm(x = data_continuous$NumWebVisitsMonth, # treatment 
             mean = fitted.values(mod_num), # fitted values
             sd = summary(mod_num)$sigma) # model sigma

mod_den <- lm(NumWebVisitsMonth ~ Year_Birth + as.factor(Education) +as.factor(Marital_Status)+ Kidhome + Teenhome + Recency + NumDealsPurchases, data = data_continuous)

den <- dnorm(x = data_continuous$NumWebVisitsMonth, # treatment variable
             mean = fitted.values(mod_den), # fitted values
             sd = summary(mod_den)$sigma)

data_continuous <- data_continuous %>%
  mutate(ipw_s = num/den)

#summary(data_continuous$ipw_s)
```

```{r, results='hide'}
ggplot(data_continuous, aes(ipw_s)) +
  geom_density(col = "#E69F00", fill = "#E69F0095") + 
  scale_x_log10() + 
  theme_minimal(base_size = 20) + 
  xlab("Stabilized Weights")+ geom_vline(xintercept = median(data_continuous$ipw_s), linetype="twodash", color = "red", size=0.7) +
  labs(x="Stabilized Weights", y="Density", title= "Figure 10: Distribution of Weights after IPW")
```

```{r, message=FALSE, warning=FALSE, results='hide'}
library(rsample)
library(PSW)
#fit inverse probablity weight model
fit_ipw <- function(split, ...) {
  .df <- analysis(split)
  # fit propensity score model
  mod_num <- lm(NumWebVisitsMonth ~ 1, data = .df)
  num <- dnorm(x = .df$NumWebVisitsMonth, # treatment 
             mean = fitted.values(mod_num), # fitted values
             sd = summary(mod_num)$sigma) # model sigma
  mod_den <- lm(NumWebVisitsMonth ~ Year_Birth + as.factor(Education) +as.factor(Marital_Status)+ Kidhome + Teenhome + Recency + NumDealsPurchases, data = .df)
  den <- dnorm(x = .df$NumWebVisitsMonth, # treatment variable
             mean = fitted.values(mod_den), # fitted values
             sd = summary(mod_den)$sigma)

  .df <- .df %>%
    mutate(ipw_s = num/den)

  # fit correctly bootsrapped ipw model
  # outcome model 
  lm(TotalPurchase ~ NumWebVisitsMonth, data = .df) %>% 
    tidy()
}

# fit ipw model to bootstrapped samples
ipw_results <- bootstraps(data_continuous, 1000, apparent = TRUE) %>% 
  mutate(results = map(splits, fit_ipw))
```


```{r, message=FALSE, warning=FALSE, results='hide'}
# get t-statistic-based CIs
boot_estimate <- int_t(ipw_results, results) %>%
  filter(term == c("(Intercept)", "NumWebVisitsMonth"))
boot_estimate
```




### Sensitivity Analysis {.tabset}


#### Unweighted


```{r, message=FALSE, warning=FALSE, results='hide'}
library(tipr)

adjust_coef(effect = -5.350321, smd = 0.1, outcome_association = 1.5)

```


#### ATO Weighted


```{r, message=FALSE, warning=FALSE, results='hide'}
library(tipr)

adjust_coef(effect = -3.029384, smd = 0.1, outcome_association = 1.5)

```


#### Continuous Exposure


```{r, message=FALSE, warning=FALSE, results='hide'}
library(tipr)

adjust_coef(effect = -1.26591, smd = 0.1, outcome_association = 1.5)

```



